---
title: "linear model from Web"
author: "Citlali Gonzalez"
date: "6/25/24"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# Methods

All variables are numerical, so we use num~num for all three parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS 
 
## Descriptive results--Scatter plot

```{r}
plot(SIMS~ARM,data=data)
```

This plot shows that as arm strength increases, the level of sims also rises.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation shows that a value of 0.6860073 being positive implies that as strength increases so does sims. If the correlation were negative the sims would decrease instead.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

#### scatterplot with model fit

```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph shows that the p-values for both the intercept and slope are 0.00000000000000022, leading us to reject the null hypothesis since it is smaller than 0.05.

#### Predict at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```

This numerical summary shows the sims prediction is a value of 0.7 for ARM=88, with a prediction interval of (-1.73,3.14).

## Model 2 SIM~GRIP

### Descriptive results--scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This boxplot indicates that as your grip strength increases, the sims also increase.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This numerical summary shows that a stronger grip correlates with a posotive sims outcome.

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```


#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

